Fusion Moves for Correlation Clustering

### 2014-10-24 paper/egpaper_for_review.tex
comments and data

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}
%%%%%%%%% TITLE
\include{my_macros.tex}
\title{Correlation Clustering with Dynamic Super-Nodes (DySNCC)}

@@

@@

@@

@@

\subsubsection{Multicut Objective}

The multicut / correlation clustering objective 
can be formulated in different ways.

\paragraph{Edge Indicator Variables:}
\begin{center}
    \begin{eqnarray}
        y^* &=& \argmin_{y} \sum_{ e_{ij} \in E } w_{ij} \cdot y_{ij} \\
        s.t.:& & y \in \textit{Multicut Polytope} \nonumber
    \end{eqnarray}
\end{center}

\paragraph{Fully Connected Graph:}
\begin{center}
    \begin{eqnarray}
        y^*   & = & \argmin_{y} \sum_{ i<j \in V } w_{ij} \cdot y_{ij} \\
        s.t.: &  & y_{ij} + y_{jk} < y_{i,k} \quad \forall i, j, k   \nonumber
    \end{eqnarray}
\end{center}

\paragraph{Node Coloring:}
\begin{center}
    \begin{eqnarray}
        l^* &=& \argmin_{L} \sum_{ e_{ij} \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \\
        y_{ij}^* &=& [l_{u} \neq l_{v}]  
    \end{eqnarray}
\end{center}

\subsubsection{Solver for the Multicut Objective}

@@

   \begin{itemize}
   \item Multicut~\cite{kappes_2011_emmcvpr}
   \item Expand and Explorer~\cite{bagon_2011_arxiv}
   \item Fast Planar CC~\cite{yarkony_2012_eccv}
   \item Break and Conquer \cite{alush_2013_simbad}.
   \item Cut Glue And Cut~\cite{beier_2014_cvpr}
   \end{itemize}

@@

\subsection{Karger-Stein Algorithms}
Use randomized procedure to reduce the number of nodes / edges to a reasonable 
number.
On the smaller graph, more expensive solvers are used.

%------------------------------------------------------------------------
\section{Intersection Fusion Cut}

@@

\input{inputs/fig_move_graph.tex}

@@

@@

@@

\input{tables/anytime/image-seg.tex}

\input{tables/anytime/knott-3d-150.tex}

\input{tables/knott-3d-300.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-6000:-4500,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
%\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
%\addlegendentry{HC-CGC}

@@

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-150}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-40000:-24000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-300.data};
\addlegendentry{HC-CGC}

@@

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-300}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-80000:-60000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-450.data};
\addlegendentry{HC-CGC}

@@

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-450}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-10000000:-100000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-550.data};
\addlegendentry{HC-CGC}

@@

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-550}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{figure}[H]
\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
%restrict y to domain=-10000000:-100000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/seg-3d.data};
\addlegendentry{HC-CGC}

@@

@@

\input{tables/anytime/knott-3d-450.tex}
\begin{figure}
\input{scatterplots/knott-3d-450.tex}
\caption{Values and runtime for the 8 knott-3d-450 instances. Note that we use for DYNCC a defensive stopping condition.
A more aggressive one would lead to much faster runtime with only a bit worse values.
DYNCC find solutions with less than distance 100 to the optimum a magnitude faster than the state of the art, which produce poor results on hard instances with a 1 hour time limit.
}
\end{figure}

\input{tables/knott-3d-550.tex}

\input{tables/anytime/seg-3d.tex}

\input{tables/modularity-clustering.tex}

@@

>>>>

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}
%%%%%%%%% TITLE
\include{my_macros.tex}
%\title{Correlation Clustering with Dynamic Super-Nodes (DySNCC)}
\title{Fusion Moves for Correlation Clustering}

@@

\begin{itemize}
  \item Multicut in computer vision, applications, sparse segmentation -> IMPORTANT PROBLEM
  \item Problem: Existing Methods does not scale, even CGC. - Large scale 3d problems
  \item Contribution: Fast scalable method using novel fusion moves for correlation clustering
\end{itemize}

@@

\textbf{Contribution:}

\textbf{Outline:}

@@

\subsection{Problem Formulation}
\begin{center}
    \begin{eqnarray}
        l^* &=& \argmin_{L} \sum_{ e_{ij} \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \\
        y_{ij}^* &=& [l_{u} \neq l_{v}]  
    \end{eqnarray}
\end{center}

Problem-> Ambiguity

% \subsubsection{Multicut Objective}

% The multicut / correlation clustering objective 
% can be formulated in different ways.

% \paragraph{Edge Indicator Variables:}
% \begin{center}
%     \begin{eqnarray}
%         y^* &=& \argmin_{y} \sum_{ e_{ij} \in E } w_{ij} \cdot y_{ij} \\
%         s.t.:& & y \in \textit{Multicut Polytope} \nonumber
%     \end{eqnarray}
% \end{center}

% \paragraph{Fully Connected Graph:}
% \begin{center}
%     \begin{eqnarray}
%         y^*   & = & \argmin_{y} \sum_{ i<j \in V } w_{ij} \cdot y_{ij} \\
%         s.t.: &  & y_{ij} + y_{jk} < y_{i,k} \quad \forall i, j, k   \nonumber
%     \end{eqnarray}
% \end{center}

% \paragraph{Node Coloring:}
% \begin{center}
%     \begin{eqnarray}
%         l^* &=& \argmin_{L} \sum_{ e_{ij} \in E } w_{ij} \cdot [l_{u} \neq l_{v}] \\
%         y_{ij}^* &=& [l_{u} \neq l_{v}]  
%     \end{eqnarray}
% \end{center}

@@

% \subsubsection{Solver for the Multicut Objective}

@@

\subsubsection{Correlation Clustering}
   \begin{itemize}
   \item Multicut~\cite{kappes_2011_emmcvpr}
   \item Expand and Explorer~\cite{bagon_2011_arxiv}
   \item Fast Planar CC~\cite{yarkony_2012_eccv}
   \item Break and Conquer \cite{alush_2013_simbad}.
   \item Cut Glue And Cut~\cite{beier_2014_cvpr}
   \end{itemize}

@@

% \subsection{Karger-Stein Algorithms}
% Use randomized procedure to reduce the number of nodes / edges to a reasonable 
% number.
% On the smaller graph, more expensive solvers are used.

%------------------------------------------------------------------------
\section{Correlation-Clustering-Fusion (CCF) Moves}
Motivation Using Fusion moves -> problem ambiguity

\subsection{Define Fusion on Segmentations}
\input{inputs/fig_move_graph.tex}

@@

@@

\textbf{Desired Properties}

@@

\subsection{Polyhedral Interpretation}

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[p]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=0:4600,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
%\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
%\addlegendentry{HC-CGC}

\addplot[color=red,mark=x] table[x=time,y=CGC-planar]{data/image-seg.data};
\addlegendentry{CGC-planar}

\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/image-seg.data};
\addlegendentry{MCI-CCIFD}

\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/image-seg.data};
\addlegendentry{MC-Fusion (HC-MC-CGC)}

\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/image-seg.data};
\addlegendentry{MC-Fusion (HC-CGC-CGC)}

\end{semilogxaxis}
\end{tikzpicture}
\caption{image-seg}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[p]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-6000:-4500,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
%\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
%\addlegendentry{HC-CGC}

@@

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-150}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[p]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-40000:-24000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-300.data};
\addlegendentry{HC-CGC}

@@

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-300}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[p]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-80000:-60000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-450.data};
\addlegendentry{HC-CGC}

@@

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-450}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[p]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-10000000:-100000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-550.data};
\addlegendentry{HC-CGC}

@@

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-550}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{figure}[H]
\begin{figure}[p]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
%restrict y to domain=-10000000:-100000,
restrict y to domain=-10000000:700000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/seg-3d.data};
\addlegendentry{HC-CGC}

@@

%\addplot[color=yellow,mark=o] table[x=time, y=DYNCC-HC-MC]{data/seg-3d.data};
%\addlegendentry{MC-Fusion (HC-MC)}

@@

\begin{figure}
\input{scatterplots/knott-3d-450.tex}
\caption{Values and runtime for the 8 knott-3d-450 instances. Note that we use for DYNCC a defensive stopping condition.
A more aggressive one would lead to much faster runtime with only a bit worse values.
DYNCC find solutions with less than distance 100 to the optimum a magnitude faster than the state of the art, which produce poor results on hard instances with a 1 hour time limit.
}
\end{figure}

@@

\newpage
\onecolumn
\section{Appendix}

\input{tables/anytime/image-seg.tex}
\input{tables/anytime/knott-3d-150.tex}
\input{tables/knott-3d-300.tex}
\input{tables/anytime/knott-3d-450.tex}
\input{tables/knott-3d-550.tex}
\input{tables/anytime/seg-3d.tex}
\input{tables/modularity-clustering.tex}
